Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-05-03 papers/vph_2016/response_to_review.txt

I'd like to thank the reviewer for their comments, which were
constructive and useful. I'll reply to the comments and indicate where
I have changed the manuscript below.

> Reviewer comments:

(Introduction)

> The introduction section depicts clearly the need of such a model.

(Materials & Methods)

> The second section presents a clear architecture of the platform
> components and the overall methodology. However, there is not a strong
> mathematical support of the algorithms used. The BRAHMS and SpineML
> could be just mentioned and not analysed as much, so that the gained
> space could be used for the mathematical background of the
> algorithms.

The description of BRAHMS and SpineML has been reduced. I've added the
equations governing the rate coded neural elements.

> More analysis should be performed regarding the connection
> of the Brain model and the muscular components, as it is there where
> the main novelty of the platform resides; thus, please explain
> thoroughly how the SC Map signal is converted into the 6
> time-dependent moto-neuron activation signals.

I have added additional detail to the description of the SC map -> SBG
conversion.

(Results)

> The results section contains a methodology portion regarding the
> model's training, so please consider of transferring it to the 2nd
> section.

This has been moved.

> Moreover, there is not any reference to the training data
> that were used, i.e. what exactly was the nature of the data input in
> the training process. Finally, a validation protocol of the simulated
> results is not mentioned at all, so please consider of adding any
> error metrics.

I have added a description of the data input for the training
process. I've not mentioned validation because the centroiding step,
ensures that only a single neural element drives the SC to SBG weight
maps and the range of inputs given ensures that every active element
in each weight map is trained.

> The reference section lacks of the titles of the journal papers and
> has to be revised.

I believe I have followed the short format for the bibliography, given
in the VPH2016 extended abstract template, which does not include
journal paper titles and so I have not made any changes here.

### 2017-08-11 papers/integration/omm_integ.tex
Current state of paper with most of the figures now in place

\title[Integrated brain and biomechanics]{
  Integrating brain and biomechanical models - a paradigm shift
  towards neuro-muscular control
}

\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{} % If more than 1 corr. author refer to original template
             % and fill this in

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% The sections below are for reference only.
%%%
%%% For Original Research Articles, Clinical Trial Articles, and
%%% Technology Reports the section headings should be those
%%% appropriate for your field and the research itself. It is
%%% recommended to organize your manuscript in the following sections
%%% or their equivalents for your field:
%%%
%%% Abstract, Introduction, Material and Methods, Results, and Discussion.
%%%
%%% Please note that the Material and Methods section can be placed in
%%% any of the following ways: before Results, before Discussion or
%%% after Discussion.
%%%
%%% For information about Clinical Trial Registration, please go to
%%% http://www.frontiersin.org/about/AuthorGuidelines#ClinicalTrialRegistration
%%%
%%% For Clinical Case Studies the following sections are mandatory:
%%% Abstract, Introduction, Background, Discussion, and Concluding
%%% Remarks.
%%%
%%% For all other article types there are no mandatory sections.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
\section{}
To date, realistic models of how the central nervous system governs
behaviour have been restricted in scope to the brain, brainstem or
spinal column, as if these existed as disembodied organs.
Further, the model is often exercised in relation to an in vivo
physiological experiment with input comprising an impulse, a periodic
signal or constant activation, and output as a pattern of neural
activity in one or more neural populations. Any link to behaviour is
inferred only indirectly via these activity patterns.
%
We argue that to discover the principles of operation of neural
systems, it is necessary to express their behaviour in terms of
physical movements of a realistic motor system, and to supply inputs
that mimic sensory experience. To do this with confidence, we must
connect our brain models to neuro-muscular models and provide relevant
visual and proprioceptive feedback signals, thereby closing the loop
of the simulation.
%
This paper describes an effort to develop just such an integrated
brain and biomechanical system using a number of pre-existing
models. It describes a model of the saccadic oculomotor system
incorporating a neuromuscular model of the eye and its six extraocular
muscles. The position of the eye determines how illumination of a
retinotopic input population projects information about the location
of a saccade target into the system.
%
A pre-existing saccadic burst generator model was incorporated into
the system, which generated motoneuron activity patterns suitable for
driving the biomechanical eye. The model was demonstrated to make
accurate saccades to a target luminance under a set of environmental
constraints.
%
Challenges encountered in the development of this model showed the
importance of this integrated modelling approach. Thus, we exposed
shortcomings in individual model components which were only apparent
when these were supplied with the more plausible inputs available in a
closed loop design. Consequently we were able to suggest missing
functionality which the system would require to reproduce more
realistic behaviour.
%
The construction of such closed-loop animal models constitutes a new
paradigm of {\em computational neurobehaviour} and promises a more
thoroughgoing approach to our understanding of the brain's function as
a controller for movement and behaviour.

@@

% A very short introduction to the section.
The integrated brain and biomechanical model described here is a
development of the model in \mycite{alex_cope_integrative_2015},
referred to here as the \ccg~model. This was a rate-coded neural
network model incorporating retinal populations, frontal eye fields
(FEF), the basal ganglia (BG), and the superior colliculus (SC). In
the \ccg~model, the ``centre of mass'' of the activity in the deep
layers of superior colliculus was assumed to accurately encode the
location of the eye at the end of the saccade~\cite{someone}. This
location was used to recalculate the positions of the luminances in
the eye's frame of reference at each time step. The model included no
brainstem populations other than superior colliculus, nor a
neuromuscular model.

To the \ccg~model, we have added a brainstem model (a ``saccadic burst
generator''), and a biomechanical eye. These will be described below,
but first we will give an explanation of the modelling framework used.

@@

In the current work, the \ccg~model was reproduced using the
declarative SpineML markup language (\mycite{richmond_model_2014}),
with the help of the graphical SpineML model editing software
called SpineCreator
(\mycite{cope_spinecreator:_2016}). SpineML,
which is a development of the NineML specification
(\mycite{incf_task_force_on_multi-scale_modeling_network_2011}),
describes neural populations and their projections in a highly
structured format in which neuron bodies, pre- and post-synapses are
described in terms of \e{SpineML components}. These are similar to the
components provided by BRAHMS, but in this case, the components are an
XML description of the functionality of the component, rather than a
programmatic implementation, with one XML file per component. A
SpineML \e{network layer} file then describes which components are
used in the model, and how they are connected together. Finally, a
number of SpineML \e{experiment layer} files describe how the model
described in the network layer can be executed. In the experiment
layer, the execution duration and timestep can be specified, along
with input conditions, connection lesions and component parameter
updates. A complete description of SpineML is given
in \mycite{richmond_model_2014}.

SpineCreator, in its r\^ole as a graphical editor for the SpineML
format, was used to generate the SpineML files describing the
model. It was also used to generate the diagrams of the model
(e.g. Fig.~\ref{brain_model}).

As a declarative format for model specification, SpineML is agnostic
about how the model is executed. A number of SpineML simulation
engines exist, including DAMSON (\mycite{richmond_damson_2015}), GeNN
(\mycite{nowotny_flexible_2011,nowotny_spineml_2014}) and BRAHMS (used
here). The simulation engine for BRAHMS is called \stob~
(\mycite{cope_spineml_2_brahms_2015-1}). \stob~is a collection of XSLT
stylesheets which first generate and compile C++ BRAHMS components
from the SpineML component layer description files. \stob~then uses
the SpineML network and experiment layer files to generate a BRAHMS
SystemML description of the model. Finally, \stob~executes the model,
now described entirely as a BRAHMS system, via a call to the BRAHMS
binary. A number of additional hand-written components are present
in \stob~providing the inputs (constant inputs, time-varying inputs,
etc) which the modeller specifies in the experiment layer.

In addition to the brain model components, all of which are
code-generated using \stob~as described above, three hand-written
components are integrated into the model: The biomechanical eye model;
a component which computes the centroid of a neural layer; and a
component which takes as inputs the eye's rotational state and the
state of the experimental luminances and projects a retinotopic
activity map into the brain model. Each of these three BRAHMS
components was hand written in C++. To incorporate these components
into the present integrated model, a model-specific modification was
made to the scripts in \stob~(\mycite{cope_spineml_2_brahms_2015}).

Figure \ref{model_framework} shows the workflow, in which the model
specification files (blue box), a combination of SpineML files and C++
code, are processed (green box) into a BRAHMS system (red box).

@@

The brain model, excluding the brainstem, is a re-implementation of
the \ccg~model. Figure \ref{brain_model} shows the layout of the
populations and the interconnections between them. Each population of
2500 elements is arranged as a 50 by 50 grid which forms a map in a
retinotopic co-ordinate system, roughly matching the known layout of
the superior colliculus (SC). % FIXME: and frontal eye field?

@@

(\mycite{robinson_eye_1972}). With the exceptions of the World and
FEF\_add\_noise populations, each neural element represents an
activation whose dynamics depend on the component definition. In the
brain model, there are six different components in use; LINlinear,
LINlinearNoisy, LINret, LINexp, D1MSN and D2MSN.

The LINlinear component governs the activation $a$ with a first order
leaky integrator differential equation:
\[
   \dot{a} = {1 \over \tau}(a_{in}-a)
\]
where $\tau$ is the time constant for the neural activation and
$a_{in}$ is the input to the neural element. $a_{in}$ is defined by an
activation input and a shunting inhibition input according to:
\[
   a_{in} = A(1-s_a)+0.01 R_N
\]
Here, $A$ is the activation input and $s_a$ is the shunting inhibition
state variable whose value is related to the shunting input, $S$ by
\[
   s_a = \begin{cases}
      S & S\leq 1 \\
      1 & S > 1
   \end{cases}
\]
$R_N$ is a random number between 0 and 1 drawn from a
normal distribution and introduces noise to the activation of the
neural element.

The output, $y$, of LINlinear is related to the activation by the
piecewise linear transfer function
\[
   y(a) = \begin{cases}
      0   & a < c \\
      a-c & c \leq a \leq 1+c \\
      1   & a > 1+c
   \end{cases}
\]
where $c$ is a parameter defining the slope of the transfer
function. At this point, the naming scheme for the component becomes
apparent; this is a Leaky Integrator with a linear transfer function.

@@

Each population of 2500 neural elements is arranged in a 50 by 50
grid, with positions on the grid representing a retinotopic
mapping. Locations on the grid specify radial and azimuthal angles r
and $\phi$ for the location of activity on the retina relative to the
fovea. r and $\phi$ can be converted into rotations about the $x$ and
$y$ Cartesian axes ($\theta_x$ and $\theta_y$). The result of a
positive rotation about the $x$ axis in a right-handed Cartesian
coordinate system results in an "upward movement" of the fovea's view
of the environment. Note that a positive rotation about the $y$ axis
results in a "leftward movement".

@@

Figure \ref{mapping} shows the result of the mapping for a view of two
cross-shaped luminances. One cross illuminates the fovea, which
results in a large comb-shape of activity. The more peripheral cross
produces an indistinct object centered at a larger value of r.

It is important to note that in practice there are edge effects within
the model which prevent this theoretical mapping from holding
perfectly. The most significant of these is the result of the diffuse
excitation from STN to GPe... etc % FIXME Where are the edge effects
                                  % most prevalent? In BG I think

@@

Briefly, the model consists of input from the World population
producing activity in an ``express'' pathway to superior colliculus
and simultaneously in cortex, represented here by the FEF
population. The express pathway causes short latency activity in the
superficial superior colliculus, which directly innervates the deeper
layers of the superior colliculus (SC\_deep). Activity in FEF
generates firing in a thalamo-cortico-basal ganglia loop. The output
of the basal ganglia is the substantia nigra pars reticulata (SNr)
which tonically inhibits SC\_deep. If a location of activity in FEF is
able to dominate selection in the basal ganglia circuit, the
corresponding location in SNr will dis-inhibit and activity will build
up in SC\_deep encoding the saccade end point.

Connections shown in red are one to one connections; dark blue
connections indicate a connectivity pattern which ``fans out'' with a 2-D
Gaussian kernel; lighter blue connections from STN to SNr and GPe are
diffuse, all to all connections and connections in green are one to one
connections that decay towards the fovea so that foveal activity in
FEF does not swamp the basal ganglia which would prevent peripheral
luminances from being selected.

Note that SC\_deep contains two recurrent connections; one is
excitatory, with a Gaussian kernel mapping and the other implements
tecto-tectal inhibition, which increases the inhibition between
activity in opposite hemispheres of the field of view (refs). The
tecto-tectal inhibitory connection is \em{not} present in the \ccg
model.

@@

Neurons in the deep layers of the superior colliculus called long lead
burst neurons innervate excitatory burst neurons in the reticular
formation (ref). In this model, we implement a network based
on \mycite{gancarz_neural_1998}.

@@

Patras work here.

% Section - description of the integration
\subsection{Integrating the models}

@@

% trajectories, neuron activations (esp. brainstem). latency vs
% dopamine, latency vs gap.

@@

SJ, AB and AC implemented existing parts of the model in SpineML. AB
developed the saccade generator brainstem model. SJ performed the
technical integration of the biomechanical eye. DS, CP and KM
developed the biomechanical eye model. SJ wrote the manuscript. KG
conceived the experiment. % FIXME: This needs correcting/developing.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/intro_graphic.png}
\end{center}
\textbf{\refstepcounter{figure}\label{intro_graphic} Figure \arabic{figure}.}
{ An isolated brain model. Crafted inputs are introduced into one of
the model's n state variables. The output of another of the state
variables implies behavioural change or onset.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
\end{center}
\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
{ The model framework. The model is specified using a combination of
declarative XML files and hand-coded C++. These original model
specifications are shown within the blue box. b) The green box shows
the processes which are applied to the model specification to produce
the BRAHMS system. Most of the process is defined within the scripts
which make up \stob, but the three hand-written components must be
manually compiled and installed within the BRAHMS Namespace, allowing
the BRAHMS executable to locate them at runtime. c) The red box shows
the resulting BRAHMS system ready to be executed by the BRAHMS
executable. In practice, this call is made by \stob.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
\end{center}
\textbf{\refstepcounter{figure}\label{mapping} Figure \arabic{figure}.}
{ Representative mapping from eye's frame of reference in cartesian
coordinates to retinotopic coordinates. (a) The mapping of luminances
in the eye's frame of reference. The world input is pre-defined by a
JSON configuration file. luminance position, size and shape can be
defined in this file, along with the times at which luminances appear
and disappear. The worldDataMaker.cpp code computes the locations of
the luminances in the eye's frame of reference, given its rotational
state. Here, there are two cross shaped luminances, one at the
fixation point (0,0) and one at a peripheral position (4,-10). (b) The
locations of the luminances in the eye's frame of reference are then
converted into retinotopic coordinates, with centrally located
luminances being represented at low values of $r$ and more peripheral
luminances having higher values of $r$. $phi$ encodes rotational
angle: 12.5 is up, [etc etc]. The output of the World component is fed
into FEF\_add\_noise and into the retinal neuron populations. (c) The
FEF\_add\_noise populations adds a level of noise to the signal
representing processing of the signal in visual cortex. (d) The
activity in FEF is the input to the basal ganglia and one input to
superior collicus.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{brain_model} Figure \arabic{figure}.}
{ This is the Brain Model}
\end{figure}

>>>>

\title[Integrated brain and biomechanics]{
Integrating brain and biomechanical models - a new paradigm
for understanding  neuro-muscular control
}

\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{} % If more than 1 corr. author refer to original template
             % and fill this in
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% The sections below are for reference only.
%%%
%%% For Original Research Articles, Clinical Trial Articles, and
%%% Technology Reports the section headings should be those
%%% appropriate for your field and the research itself. It is
%%% recommended to organize your manuscript in the following sections
%%% or their equivalents for your field:
%%%
%%% Abstract, Introduction, Material and Methods, Results, and Discussion.
%%%
%%% Please note that the Material and Methods section can be placed in
%%% any of the following ways: before Results, before Discussion or
%%% after Discussion.
%%%
%%% For information about Clinical Trial Registration, please go to
%%% http://www.frontiersin.org/about/AuthorGuidelines#ClinicalTrialRegistration
%%%
%%% For Clinical Case Studies the following sections are mandatory:
%%% Abstract, Introduction, Background, Discussion, and Concluding
%%% Remarks.
%%%
%%% For all other article types there are no mandatory sections.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\begin{abstract}

\section{}
To date, realistic models of how the central nervous system governs
behaviour have been restricted in scope to the brain, brainstem or
spinal column, as if these existed as disembodied organs.
Further, the model is often exercised in relation to an in vivo
physiological experiment with input comprising an impulse, a periodic
signal or constant activation, and output as a pattern of neural
activity in one or more neural populations. Any link to behaviour is
inferred only indirectly via these activity patterns.
%
We argue that to discover the principles of operation of neural
systems, it is necessary to express their behaviour in terms of
physical movements of a realistic motor system, and to supply inputs
that mimic sensory experience. To do this with confidence, we must
connect our brain models to neuro-muscular models and provide relevant
visual and proprioceptive feedback signals, thereby closing the loop
of the simulation.
%
This paper describes an effort to develop just such an integrated
brain and biomechanical system using a number of pre-existing
models. It describes a model of the saccadic oculomotor system
incorporating a neuromuscular model of the eye and its six extraocular
muscles. The position of the eye determines how illumination of a
retinotopic input population projects information about the location
of a saccade target into the system.
%
A pre-existing saccadic burst generator model was incorporated into
the system, which generated motoneuron activity patterns suitable for
driving the biomechanical eye. The model was demonstrated to make
accurate saccades to a target luminance under a set of environmental
constraints.
%
Challenges encountered in the development of this model showed the
importance of this integrated modelling approach. Thus, we exposed
shortcomings in individual model components which were only apparent
when these were supplied with the more plausible inputs available in a
closed loop design. Consequently we were able to suggest missing
functionality which the system would require to reproduce more
realistic behaviour.
%
The construction of such closed-loop animal models constitutes a new
paradigm of {\em computational neurobehaviour} and promises a more
thoroughgoing approach to our understanding of the brain's function as
a controller for movement and behaviour.

@@

% A very short introduction to the section.
The integrated brain and biomechanical model described here is a
development of the model in \mycite{alex_cope_integrative_2015},
referred to here as the \ccg~model. This was a rate-coded neural
network model incorporating retinal populations, frontal eye fields
(FEF), the basal ganglia (BG), and the superior colliculus (SC). In
the \ccg~model, the centroid of the activity in the deep
layers of superior colliculus was assumed to accurately encode the
location of the eye at the end of the
saccade~(\cite{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}).
This location was used to recalculate the positions of the luminances in
the eye's frame of reference at each time step. The model included no
brainstem populations other than superior colliculus, nor a
neuromuscular model.

To summarize, the \ccg~model takes as \emph{input} the positions of luminances on a topographic map and produces as output a saccade target.

To the \ccg~model, we have added a rate-coded brainstem model (a ``saccadic burst
generator''), and a biomechanical eye, implemented using the biomechanical modelling framework OpenSim. These will be described below,
but first we will give a description of the modelling framework used.

@@

In the current work, the \ccg~model was reproduced using the
declarative SpineML markup language (\mycite{richmond_model_2014}),
with the help of the graphical SpineML model editing software
called SpineCreator
(\mycite{cope_spinecreator:_2016}). SpineML,
which is a development of the NineML specification
(\mycite{incf_task_force_on_multi-scale_modeling_network_2011}),
describes neural populations and their projections in a highly
structured format in which neuron bodies, pre- and post-synapses are
described in terms of \e{SpineML components}. These are similar to the
components provided by BRAHMS, but in this case, the components are an
XML description of the functionality of the component, rather than a
programmatic implementation, with one XML file per component. A
SpineML \e{network layer} file then describes which components are
used in the model, and how they are connected together. Finally, a
number of SpineML \e{experiment layer} files specify how the model
described in the network layer can be executed. In the experiment
layer, the execution duration and timestep can be specified, along
with input conditions, connection lesions and component parameter
updates. A complete description of SpineML is given
in \mycite{richmond_model_2014}.

SpineCreator, in its r\^ole as a graphical editor for the SpineML
format, was used to generate the SpineML files describing the
model. It was also used to generate the diagrams of the model
(e.g. Fig.~\ref{fig:brain_model}).

As a declarative format for model specification, SpineML is agnostic
about how the model is executed. A number of simulation
engines can be utilised, including DAMSON (\mycite{richmond_damson_2015}), GeNN
(\mycite{nowotny_flexible_2011,nowotny_spineml_2014}) and BRAHMS (used
here). The simulation engine incorporating BRAHMS is called \stob~
(\mycite{cope_spineml_2_brahms_2015-1}). \stob~is a collection of XSLT
stylesheets which first generate and compile C++ BRAHMS components
from the SpineML component layer description files. \stob~then uses
the SpineML network and experiment layer files to generate a BRAHMS
SystemML description of the model. Finally, \stob~executes the model,
now described entirely as a BRAHMS system, via a call to the BRAHMS
binary. A number of additional hand-written components are present
in \stob~providing the inputs (constant inputs, time-varying inputs,
etc) which the modeller specifies in the experiment layer.

In addition to the brain model components, all of which are
code-generated using \stob~as described above, three hand-written
components are integrated into the model: The biomechanical eye model;
a component which computes the centroid of a neural layer; and a sensory input
component. The sensory input component takes the eye's rotational state and the
state of the experimental luminances as its inputs and projects a retinotopic
activity map into the brain model. Each of these three BRAHMS
components was hand written in C++. To incorporate these components
into the SpineML model, a model-specific modification was
applied in \stob~(\mycite{cope_spineml_2_brahms_2015}) making use of a \stob~feature designed for this purpose (The external.xsl file).

%\footnote{See the \branch{NoTremor\_Oculomotor\_201603} branch of \url{https://github.com/SpineML/SpineML\_2\_BRAHMS/}}.

Figure \ref{fig:model_framework} shows the workflow, in which the model
specification files (blue box), a combination of SpineML files and C++
code, are processed (green box) into a BRAHMS system (red box).

@@

The brain model, excluding the brainstem, is a re-implementation of
the \ccg~model. Figure \ref{fig:brain_model} shows the layout of the
populations and the interconnections between them. Each population of
2500 elements is arranged as a 50 by 50 grid which forms a map in a
retinotopic co-ordinate system, roughly matching the known layout of
the superior colliculus~(\mycite{robinson_eye_1972}). % FIXME: and frontal eye field?

@@

With the exceptions of the World and
FEF\_add\_noise populations, each neural element represents an
activation whose dynamics depend on the component definition. In the
brain model, there are six different components in use; LINlinear,
LINlinearNoisy, LINret, LINexp, D1MSN and D2MSN.

The LINlinear component governs the activation $a$ with a first order
leaky integrator differential equation:
\[
   \dot{a} = {1 \over \tau}(a_{in}-a)
\]
where $\tau$ is the time constant for the neural activation and
$a_{in}$ is the input to the neural element. $a_{in}$ is defined by an
activation input and a shunting inhibition input according to:
\[
   a_{in} = A(1-s_a)+0.01 R_N
\]
Here, $A$ is the activation input and $s_a$ is the shunting inhibition
state variable whose value is related to the shunting input, $S$ by
\[
   s_a = \begin{cases}
      S & S\leq 1 \\
      1 & S > 1
   \end{cases}
\]
$R_N$ is a random number drawn from a
standard normal distribution ($\sigma$=1, $\mu$=0) and introduces noise
to the activation of the neural element.

The output, $y$, of LINlinear is related to the activation $a$ by the
piecewise linear transfer function
\[
   y(a) = \begin{cases}
      0   & a < c \\
      a-c & c \leq a \leq 1+c \\
      1   & a > 1+c
   \end{cases}
\]
where $c$ is a parameter defining the slope of the transfer
function. At this point, the naming scheme for the component becomes
apparent; this is a Leaky Integrator with a linear transfer function.

@@

Each population of 2500 neural elements is arranged in a 50 by 50
grid, with positions on the grid representing a retinotopic
mapping. Locations on the grid specify radial and azimuthal angles r
and $\phi$ for the location of activity on the retina relative to the
fovea. r and $\phi$ can be converted into rotations about the $x$ and
$y$ Cartesian axes ($\theta_x$ and $\theta_y$). The result of a
positive rotation about the $x$ axis in a right-handed Cartesian
coordinate system results in an upward movement of the fovea's view
of the environment. Note that a positive rotation about the $y$ axis
results in a \emph{leftward} movement.

Note that the mapping encompases the entire visual field. The value of
$\phi$ is allowed to vary from 0 to 360\degrees along its axis.
Effectively, the two contralateral colliculi are incorporated into a
single, square map, avoiding the need to carry out `colliculus
gluing'~\cite{tabareau_geometry_2007}.

@@

Figure \ref{fig:mapping} shows the result of the mapping for a view of two
cross-shaped luminances. One cross illuminates the fovea, which
results in a large comb-shape of activity. The more peripheral cross
produces an indistinct object centered at a larger value of r.

@@

Briefly, the model consists of input from the World population
producing activity in an `express' pathway to superior colliculus
and simultaneously in cortex, represented here by the FEF
population. The express pathway causes short latency activity in the
superficial superior colliculus, which directly innervates the deeper
layers of the superior colliculus (SC\_deep). Activity in FEF
generates firing in a thalamo-cortico-basal ganglia loop. The output
of the basal ganglia is the substantia nigra pars reticulata (SNr)
which tonically inhibits SC\_deep. If a location of activity in FEF is
able to dominate selection in the basal ganglia circuit, the
corresponding location in SNr will dis-inhibit and activity will build
up in SC\_deep encoding the saccade end point.

Connections shown in red are one to one connections; dark blue
connections indicate a connectivity pattern which `fans out' with a 2-D
Gaussian kernel; lighter blue connections from STN to SNr and GPe are
diffuse, all to all connections and connections in green are one to one
connections that decay towards the fovea so that foveal activity in
FEF does not swamp the basal ganglia which would prevent peripheral
luminances from being selected.

Note that SC\_deep contains two recurrent connections; one is
excitatory, with a Gaussian kernel mapping and the other implements
tecto-tectal inhibition, which increases the inhibition between
activity in opposite hemispheres of the field of view (refs). The
tecto-tectal inhibitory connection is \emph{not} present in the \ccg
model.

@@

Neurons in the deep layers of the superior colliculus called long lead
burst neurons innervate excitatory burst neurons in the reticular
formation (ref). In this model, we implement a network based
on \cite{gancarz_neural_1998}.

@@

% Possibly introductory paragraph here.

% Patras - what about a figure here?

% EYE MODEL DESCRIPTION HERE
The biomechanical eye model, implemented using the OpenSim framework
\cite{seth_opensim:_2011}, is anatomically represented by a sphere of
uniform mass distribution. The diameter of the eye is 24 mm for adults,
with small variations between individuals; the mass of the eye is 7.5 grams.
The eyeball is actuated by six extraocular muscles
(EOMs). The EOMs are arranged in three pairs forming a cone inside the
orbit with the apex being located inside the cranium in a tendonous
ring called the annulus of Zinn. An important feature of the
oculomotor system which greatly affects its overall behavior is the
existence of dynamic EOM pulleys. Their role is to guide the pivot
point of the EOMs. In our model, a pulley for each EOM has been
modeled by a point on the orbit whose location depends on the current
eye orientation.

%EOM dynamics
The force applied by EOMs is controlled by an excitatory signal
supplied by motoneurons in the brainstem. The dynamics of muscular
forces can be split into: 1) The elasticity of the muscles. 2) A delay
between the onset of the afferent excitatory signal and the actual
muscle contraction, caused by the transmission time of the action
potentials and by the necessary calcium release at the muscle
fibres. We developed a custom extraocular muscle model which captures
these features.

%Orbital fat force
Passive forces due to the fatty tissues inside the eye orbit also
affect eye dynamics. Their role is critical in eliminating the
influence of head and body movements. We incorporated a custom torque, $\mathbf{t}$,
which acts like a rotational spring-damper apparatus, resisting
eyeball movements. It has elastic and viscous properties governed by
$\mathbf{t} = -K\mathbf{R}-C\mathbf{U}$ where $\mathbf{R}$ is the
eye's orientation and $\mathbf{U}$ is its angular velocity. $K$ and
$C$ are constants.

% Section - description of the integration
\subsection{Integrating the models and closing the loop}

@@

% trajectories, neuron activations (esp. brainstem). latency vs
% dopamine, latency vs gap.
%
% The importance of an even sized hill of activity in SC_deep. The difficulties of achieving this.

@@

SJ, AB and AC implemented existing parts of the model in SpineML. AB
developed the saccade generator brainstem model. SJ performed the
technical and scientific integration of the biomechanical eye.
DS, CP and KM developed the biomechanical eye model. SJ wrote the 
manuscript. KG conceived the experiment. % FIXME: This needs correcting/developing.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/intro_graphic.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:intro_graphic} Figure \arabic{figure}.}
{ \textbf{fig:intro\_graphic} An isolated brain model. Crafted inputs are introduced into one of
the model's n state variables. The output of another of the state
variables implies behavioural change or onset.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:model_framework} Figure \arabic{figure}.}
{ \textbf{fig:model\_framework} The model framework. The model is specified using a combination of
declarative XML files and hand-coded C++. These original model
specifications are shown within the blue box. b) The green box shows
the processes which are applied to the model specification to produce
the BRAHMS system. Most of the process is defined within the scripts
which make up \stob, but the three hand-written components must be
manually compiled and installed within the BRAHMS Namespace, allowing
the BRAHMS executable to locate them at runtime. c) The red box shows
the resulting BRAHMS system ready to be executed by the BRAHMS
executable. In practice, this call is made by \stob.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
{ \textbf{fig:mapping} Representative mapping from eye's frame of reference in cartesian
coordinates to retinotopic coordinates. (a) The mapping of luminances
in the eye's frame of reference. The world input is pre-defined by a
JSON configuration file. luminance position, size and shape can be
defined in this file, along with the times at which luminances appear
and disappear. The worldDataMaker.cpp code computes the locations of
the luminances in the eye's frame of reference, given its rotational
state. Here, there are two cross shaped luminances, one at the
fixation point (0,0) and one at a peripheral position (4,-10). (b) The
locations of the luminances in the eye's frame of reference are then
converted into retinotopic coordinates, with centrally located
luminances being represented at low values of $r$ and more peripheral
luminances having higher values of $r$. $phi$ encodes rotational
angle: 12.5 is up, [etc etc]. The output of the World component is fed
into FEF\_add\_noise and into the retinal neuron populations. (c) The
FEF\_add\_noise populations adds a level of noise to the signal
representing processing of the signal in visual cortex. (d) The
activity in FEF is the input to the basal ganglia and one input to
superior collicus.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/Brain_Stem_1channel.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:sbg} Figure \arabic{figure}.}
{ \textbf{fig:sbg} One pair of channels of the saccadic burst generator (SBG) for left (cyan)
or right (green) movements. Collicular activity in SC\_avg excites the channels
via SBG weight maps. Each box represents a neural population and shows the
population name, the number of neural elements (here 2500 or 1) and the SpineML
component name; \emph{LIN} for Leaky integrator or \emph{integrator}. Key: LLBN:
Long lead burst neurons; IBN: Inhibitory burst neurons; OPN: Omnipause neurons;
EBN: Excitatory burst neurons; TN: Tonic neurons; MN: Motoneurons.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:brain_model} Figure \arabic{figure}.}
{ \textbf{fig:brain\_model}  The brain model. This is the SpineCreator `network layer' view of the model. Each box represents a neural population with 2500 elements, arranged in a 50$\times$50 grid. The SpineML component name is printed on the bottom right corner of each population box and the population name is at the top. The overall connectivity between populations is represented by the projection arrows with the colour indicating the connectivity scheme (one-to-one connections are red, gaussian kernel connections are dark blue and so on). Excitatory connections have arrowheads and inhibitory connections have circles, although for details of the behaviour of the connections, the weight-update and post-synapse components must be studied. Briefly, the model comprises a \emph{World} population, into which a retinotopically organised view of the world is introduced. This information is passed into cortical populations (FEF) and subcortical populations (SC) via a simple model of the retina. These feed a cortico-thalamo-basal ganglia loop, which selects which region of the deep layer of superior colliculus should be disinhibited, allowing activity to build up therein. The five populations comprising the basal ganglia are enclosed in a grey outline. Note that substantia nigra pars compacta is not modelled here, instead the level of dopamine in the striatum is set via a parameter in the Str\_D1 and Str\_D2 populations}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/weightmaps.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:weightmaps} Figure \arabic{figure}.}
{ \textbf{fig:weightmaps} Weight maps}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outmany.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:outmany} Figure \arabic{figure}.}
{ \textbf{fig:outmany} Representative single saccades.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:sacc_vs_targ} Figure \arabic{figure}.}
{ \textbf{fig:sacc\_vs\_targ} Accuracy at different target eccentricities for fixation luminance 0.2 and target luminance 0.3.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outrtn.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:outrtn} Figure \arabic{figure}.}
{ \textbf{fig:outrtn} There and back - a saccade to a target, followed by return to the original fixation.}
\end{figure}
